### 2024-02-29 manuscript.Rmd
minor fix BRM revision

### 1.2.2	Statistical Power for Model Comparison 
A second question that is of interest for many researchers – especially in developmental cognitive neuroscience – pertains to identifying the one theoretical model (from a set of competing models) that best explains the given data [@henson_2016; @miller_2012; @nyberg_1994]. In the case of competing models that are nested, the analytical approach to this question (and therefore also considerations on statistical power) can be addressed analogously to the procedure outlined above [see @jobst_2021 for a step-by step tutorial]. However, comparing non-nested models prohibits the use of traditional $\chi^2$-based statistics and therefore poses additional methodological challenges in determining the ‘best’ model. Nevertheless, researchers should strive for a methodological approach that matches the theoretical assumptions, rather than vice versa, that is, moving away from well-grounded theoretical considerations to meet methodological constraints. In cases where analytical solutions to questions of statistical properties like statistical power are not available, randomization-based techniques offer an excellent alternative [@efron_1994]. In particular, Monte Carlo simulations have proven useful to bridging this gap [@muthen_2002, see Section 2.1 for more details on Monte Carlo simulations].

>>>>

### 1.2.2	Statistical Power for Model Comparison 
A second question that is of interest for many researchers – especially in developmental cognitive neuroscience – pertains to identifying the one theoretical model (from a set of competing models) that best explains the given data [@henson_2016; @miller_2012; @nyberg_1994]. In the case of competing models that are nested, the analytical approach to this question (and therefore also considerations on statistical power) can be addressed analogously to the procedure outlined above [see @jobst_2021 for a step-by step tutorial]. However, comparing non-nested models prohibits the use of traditional $\chi^2$-based statistics and therefore poses additional methodological challenges in determining the ‘best’ model. Nevertheless, researchers should strive for a methodological approach that matches the theoretical assumptions, rather than vice versa, that is, moving away from well-grounded theoretical considerations to meet methodological constraints. In cases where researchers aim to derive estimates of statistical power for non-nested model comparisons, randomization-based techniques offer an excellent alternative [@efron_1994]. In particular, Monte Carlo simulations have proven useful to bridging this gap [@muthen_2002, see Section 2.1 for more details on Monte Carlo simulations].
